\huge A Better (One-Line!) Title Here

### 2016-10-21 pets2017-paper/pets2017-paper.tex
add subsections to design section.
move all-participant-edges to appendix.

{\color {blue}
Introduction to security design principles.

@@

Usability design principles: 
\begin{enumerate}
\item minimal user work
\item full user control  
\item targeted user feedback
\item build a mental model
\end{enumerate}

Introduction to design changes.  \\

@@

\subsection{Results} 
{\color {red} 
The possible interface version and environment combinations resulted in 6 experimental conditions. We recruited 124 participants to aim for about 20 participants per condition. We filtered participants who downloaded their own version of Tor Browser or did not sign the consent form, resulting in 114 participants. Table~\ref{table:participant-summary} summarizes the rate of success, time to success, and active time for our participants' by condition.

@@

We summarize each participant's actions throughout the experiment in Fig.~\ref{fig:all-participant-edges}.
%and summarize where they spent their time in Appendix~\ref{all-participant-times}. 
Each row in Fig.~\ref{fig:all-participant-edges} corresponds to a participant. The bar represents a path through the interface, illustrating time spent on each screen, transitions between screens, how many attempts were made, and if they were eventually successful.

\begin{figure*}
\centering
% This is a manually edited version of the automatically generated
% all-participant-edges graphic. It is edited to have better scale labels for
% the treatments.
\includegraphics{all-participant-edges}
\caption{
Summary of participants' actions throughout the entire experiment.
Different colors indicate which screen was shown at each moment.
The ``not running'' times are those when Tor Launcher was closed;
i.e., a participant was doing something else
such as searching the web in another browser.
The overall length of the lines show the total time to completion,
except for those we cut off after approximately 40 minutes.
}
\label{fig:all-participant-edges}
\end{figure*}

@@

>>>>

{\color {blue}
Introductory sentence.
}

\subsection{Procedure} 
{\color {blue}
Talk about iteration and how we designed it here.
}

\subsection{Design Princples} 
{\color {blue}
Introduce design principles.

@@

Usability design principles: 
\begin{enumerate}
\item minimal user work
\item full user control  
\item targeted user feedback
\item build a mental model
\end{enumerate} 
}

\subsection{Design Changes} 
{\color {blue}
Introduction to design changes.  \\

@@

\subsection{Results} 
{\color {red} 
The possible interface version and environment combinations resulted in 6 experimental conditions. We recruited 124 participants to aim for about 20 participants per condition. We filtered participants who downloaded their own version of Tor Browser or did not sign the consent form, resulting in 114 participants. Table~\ref{table:participant-summary} summarizes the rate of success, time to success, and active time for our participants' by condition. Appendix~\ref{all-participant-edges}'s Fig.~\ref{fig:all-participant-edges} summarizes invididual participants' actions throughout the experiment.

@@

@@

\section{Quantitative Summary}
\label{all-participant-edges} 
\begin{figure*}
\centering
% This is a manually edited version of the automatically generated
% all-participant-edges graphic. It is edited to have better scale labels for
% the treatments.
\includegraphics{all-participant-edges}
\caption{
Summary of participants' actions throughout the entire experiment.
Different colors indicate which screen was shown at each moment.
The ``not running'' times are those when Tor Launcher was closed;
i.e., a participant was doing something else
such as searching the web in another browser.
The overall length of the lines show the total time to completion,
except for those we cut off after approximately 40 minutes.
}
\label{fig:all-participant-edges}
\end{figure*}
